The \frb\ Campaign: Multi-Observatory Radio Burst and Implications for the FRB Population

### 2017-03-17 repeater-vladata.tex
reworking table. adding errors to dm, dt

\subsection{Multi-Observatory Burst Spectrum}
Four of the VLA bursts were observed simultaneously with Arecibo and AMI-LA, while two were observed simultaneously with all four observatories (Figure \ref{fig:multi}). Of these bursts, only one VLA burst (on MJD 57648) was simultaneously detected by another observatory (Arecibo). The VLA and Arecibo burst detections had significances of 25$\sigma$\ and 39$\sigma$, respectively. The VLA and Arecibo integrated flux densities were 111 mJy and 14 mJy, respectively.

Figure \ref{fig:sgram} shows a dynamic spectrum for the 57648 burst with the VLA and AO data aligned in time. The temporal resolution of the VLA data (5~ms) is much coarser than that of Arecibo, so data were resampled to the same temporal grid after correcting for barycentric and dispersion measure offsets. The dispersion correction for both data sets assumed a DM of 560.5 pc cm$^{-3}$, which was typical of the source during the observing campaign \citep{WEIRD}. The regridded dynamic spectrum has an apparent DM error that is evident either as a frequency-dependent time drift within the Arecibo observation or in the relative alignment of Arecibo and the VLA bursts. Both of these drifts are consistent with an effective DM (i.e., one that maximizes the detection S/N ratio) of $sim$562 pc cm$^{-3}$.

@@

\begin{figure*}[htb]
\begin{center}
 \includegraphics[width=1.9\columnwidth]{aovla_spec.png}
 \caption{Composite dynamic specrum for the burst from \frb\ on MJD 57648 with data from the VLA and Arecibo observatories. Both data sets have been barycentered and corrected for an assumed dispersion measure of 560.5 pc $^{-3}$. The black line separates data from the VLA (2.5 to 3.5~GHz) and Arecibo (1.0 to 1.8~GHz). The Arecibo to VLA gain ratio is assumed to be 10.
 \label{fig:sgram}}
\end{center}
\end{figure*}

@@

\begin{table*}
\caption{Properties of Bursts from \frb **update**}
\centering
\begin{tabular}{lccccccccc}
\hline
Date                & S$_{\rm{I,int}}$  & Image S/N & E$_{\rm{int}}$ & DM$_{\rm{opt}}$ & dt & S$_{\rm{I,peak}}$ & Center & FWHM & S$_{\rm{V}}$ \\
(MJD)               & (mJy)           &           & ($10^{38}$\ erg) & (pc cm$^{-3})$ & (ms) & (mJy) & (GHz)  & (MHz) & (mJy) \\ \hline
57623.74402686      & 194             & 38        & 11 & 562.1 & & 690 & 2.8 & 290 & +3 \\ % 7.8  & 562.5 & 460 & 2.8 & 300 & +3 \\
57633.67986367      & 1500            & 179       & 97 & 561.3 & & 3350 & 3.2 & 510 & --35 \\ % 65   & 561.4 & 2200 & 3.2 & 520 & --35 \\
57633.69515938\tablenotemark{a} & 69  & 15        & 7 & 555.8 & & $>$430 & $<$2.5 & 290 & +2 \\ % 5.9  & 555.4 & $>$320 & $<$2.5 & $>$320 & +2 \\
57638.49937435      & 55              & 12        & 3 & 558.6 & & 130 & 3.1 & 410 & +5 \\ % 1.8  & 554.9 & 70 & 3.1 & 440 & +5 \\
57643.45730263      & 508             & 100       & 34 & 558.7 & & 1170 & 2.8 & 510 & --5 \\ % 13   & 559.3 & 440 & 2.8 & 530 & --5 \\
57645.42958602      & 64              & 13        & 4 & 555.9 & & 170 & 2.8 & 380 & +3 \\ % 2.6  & 554.1 & 50 & 2.7 & 970 & +3 \\
57646.46600650\tablenotemark{a} & 87  & 20        & 10 & 562.4 & & $>$420 & $<$2.5 & 420 & +1 \\ % 3.9  & 568.1 & $>$190 & $<$2.5 & $>$360 & +1 \\
57648.43691490\tablenotemark{b} & 111 & 25        & 7 & 557.4 & & 260 & 2.8 & 470 & +9 \\ % 2.9  & 557.8 & 110 & 2.8 & 440 & +9 \\
57649.45175697      & 167             & 36        & 12 & 559.9 & & 290 & 3.0 & 690 & +1 \\ \hline % 6.3  & 559.9 & 80 & 2.9 & 1400 & +1 \\ \hline
\end{tabular}
\tablenotetext{a}{Best-fit Gaussian is not centered in 3~GHz band, so spectral parameters are limits.}
\tablenotetext{b}{Detected simultaneously with Arecibo between 1.15 and 1.73~GHz.}
\label{tab:spec}
\end{table*}

Figure \ref{fig:spec} shows that the Stokes I spectra are generally characterized by a broad, Gaussian shape with inter-channel modulation as high as 100\%. To better understand the spectra, we extracted dynamic radio spectra (time versus frequency) for 2d modeling with the MCMC sampler \emph{emcee} \citep{2013PASP..125..306F}. MCMC sampling requires a generative model for the data, so we wrote functions in Python to create 2d dynamic spectra. The dynamic spectra are modeled in the spectral domain as a Gaussian envelope and in the temporal domain by a dispersive delay (scaling as frequency squared). We further allow the pulses to have a finite temporal width. This brings the total number of parameters to 6 (Gaussian amplitude, center, width, start time, time width, and DM).

@@

 \begin{minipage}{2\columnwidth}
  \includegraphics[width=0.33\columnwidth]{spec_57646.png}
  \includegraphics[width=0.33\columnwidth]{spec_57648.png}
  \includegraphics[width=0.33\columnwidth]{spec_57649.png}
 \end{minipage}
\caption{Spectra and best-fit model for nine bursts seen by the VLA from 2.5 to 3.5~GHz. Starting at the top left (moving right and then down), they correspond to bursts on MJDs 57623, 57633.68, 57633.70, 57638, 57643, 57645, 57646, 57648, and 57649. The solid line is a best-fit Gaussian model found through probabilistic modeling. Note that bursts are detected in 5~ms images generated from dedispersed visibilities.
\label{fig:spec}}
\end{center}
\end{figure*}

This analysis differs from traditional analysis in that it simultaneously models the spectral and temporal evolution of the burst. Since the burst crosses many time-frequency pixel boundaries, the temporal modeling is sensitive to temporal properties smaller than the 5~ms integration time. Table \ref{tab:spec} shows that the typical burst width is measured as $2\pm1$~ms (95\% confidence interval); the brightest burst (57633.68) has a temporal width of $2.05\pm0.05$~ms. The burst arrival times are typically measured with a precision of 1~ms; the brightest burst arrival time is measured with a precision of $\sim50\mu$s. Note that these errors are only accurate to the degree that the model represents the data. One potential bias in the model is that we do not model scintillation effects.

@@

The top panel of Figure \ref{fig:dmmodel} shows the 95\% confidence intervals on the DM for all nine VLA bursts as a function of burst time. The burst DMs are not consistent with any single value and tend to be larger than the reference value of 560.5 pc cm$^{-3}$. The range and variance in DM observed by the VLA is similar to that reported for \frb\ in \citet{2016arXiv160308880S}. As noted before, this is consistent with the idea that the DM measured at low resolution (e.g., by the VLA) is defined by true dispersion and some intrinsic structure that changes between bursts. The VLA data demonstrate that this intrinsic DM effect is visible at frequencies near 3~GHz. Assuming a "true" DM of 560.5 pc cm$^{-3}$, the excess DM can be thought of as a frequency-dependent delay that is intrinsic to the burst with a delay rate of 1--2~ms GHz$^{-1}$.

>>>>

\subsection{Multi-Observatory Burst Spectrum}
Four of the VLA bursts were observed simultaneously with Arecibo and AMI-LA, while two were observed simultaneously with all four observatories (Figure \ref{fig:multi}). Of these bursts, only one VLA burst (on MJD 57648) was simultaneously detected by another observatory (Arecibo). The VLA and Arecibo burst detections had significances of 25$\sigma$\ and 39$\sigma$ with integrated flux densities of 111 mJy and 14 mJy, respectively.

Figure \ref{fig:sgram} shows a dynamic spectrum for the 57648 burst with the VLA and AO data aligned in time. The temporal resolution of the VLA data (5~ms) is much coarser than that of Arecibo, so data were resampled to the same temporal grid after correcting for barycentric and dispersion measure offsets. The dispersion correction for both data sets assumed a DM of 560.5 pc cm$^{-3}$, which was typical of the source during the observing campaign \citep{WEIRD}. The regridded dynamic spectrum has an apparent DM error that is evident both as a frequency-dependent time drift within the Arecibo observation and as an offset between the Arecibo and VLA bursts. Both of these drifts are consistent with an effective DM (i.e., one that maximizes the detection S/N ratio) of $sim$565 pc cm$^{-3}$. This is consistent with modeling of the VLA spectrum described in \S \ref{sec:spec}.

@@

\begin{figure*}[htb]
\begin{center}
 \includegraphics[width=1.9\columnwidth]{aovla_spec.png}
 \caption{Composite dynamic specrum for the burst from \frb\ on MJD 57648 with data from the VLA and Arecibo observatories. Both data sets have been barycentered and corrected for an assumed dispersion measure of 560.5 pc $^{-3}$. The black line separates data from the VLA (2.5 to 3.5~GHz) and Arecibo (1.0 to 1.8~GHz). The amplitude scale is normalized by assuming the Arecibo to VLA gain ratio is 10.
 \label{fig:sgram}}
\end{center}
\end{figure*}

@@

\begin{table*}
\caption{Properties of Bursts from \frb}
\centering
\begin{tabular}{lccccccccc}
\hline
Date                & Image S/N & S$_{\rm{I,int}}$	& S$_{\rm{V}}$ 	& E$_{\rm{int}}$ & DM$_{\rm{opt}}$ & dt 	 & S$_{\rm{I,peak}}$ & Center & FWHM \\
(MJD)               &           & (mJy) 			& (mJy) 		& ($10^{38}$\ erg)& (pc cm$^{-3})$ & (ms) & (mJy) 	& (GHz)  & (MHz) \\ \hline
57623.74402686      & 38 		& 194				& +3			& 11 			& 567$\pm2$ 		& 2.0$\pm0.2$	 		& 690 		& 2.8 		& 290 \\
57633.67986367      & 179 		& 1500				& --35 			& 98				& 568.2$\pm0.2$ 	& 2.05$\pm0.02$			& 3340 	& 3.2 		& 510 \\
57633.69515938\tablenotemark{a} & 15 & 69			& +2			& 7  			& 562$^{+4}_{-6}$ 	& 2.5$^{+0.9}_{-0.6}$	& $>$430 	& $<$2.5	& 290 \\
57638.49937435      & 12 		& 55				& +5 			& 3  			& 567$^{+7}_{-9}$ 	& 1.3$^{+1.4}_{-0.8}$	& 130 		& 3.1 		& 420 \\
57643.45730263      & 100 		& 508				& --5 			& 34 			& 565.6$^{+0.6}_{-0.5}$ & 1.9$\pm0.1$		& 1170 	& 2.8 		& 510 \\
57645.42958602      & 13 		& 64 				& +3			& 4  			& 563$^{+5}_{-4}$ 	& 1.0$\pm0.7$		 	& 170 		& 2.8 		& 380 \\
57646.46600650\tablenotemark{a} & 20 & 87			& +1			& 10 			& 569$\pm5$ 		& 2.7$^{+0.9}_{-1.4}$	& $>$420 	& $<$2.5 	& 430 \\
57648.43691490\tablenotemark{b} & 25 & 111			& +9			& 7  			& 564$\pm2$ 		& 1.4$^{+0.3}_{-0.4}$	& 260 		& 2.8 		& 470 \\
57649.45175697      & 36 		& 167				& +1			& 12 			& 567$\pm2$ 		& 2.1$\pm0.5$		 	& 290 		& 3.0 		& 690 \\ \hline
\end{tabular}
\tablenotetext{a}{Best-fit Gaussian is not centered in 3~GHz band, so spectral parameters are limits.}
\tablenotetext{b}{Detected simultaneously with Arecibo between 1.15 and 1.73~GHz.}
\label{tab:spec}
\end{table*}

Figure \ref{fig:spec} shows that the Stokes I spectra are generally characterized by a broad, Gaussian shape with inter-channel modulation as high as 100\%. To better understand the spectra, we extracted dynamic radio spectra (time versus frequency) for 2d modeling with the MCMC sampler \emph{emcee} \citep{2013PASP..125..306F}. MCMC sampling requires a generative model for the data, so we wrote functions in Python to create 2d dynamic spectra. The dynamic spectra are generated in the spectral domain as a Gaussian envelope and in the temporal domain by a dispersive delay that scales as frequency squared. We further allow the pulses to have a finite temporal width. This brings the total number of parameters to 6 (Gaussian amplitude, center, width, start time, time width, and DM).

@@

 \begin{minipage}{2\columnwidth}
  \includegraphics[width=0.33\columnwidth]{spec_57646.png}
  \includegraphics[width=0.33\columnwidth]{spec_57648.png}
  \includegraphics[width=0.33\columnwidth]{spec_57649.png}
 \end{minipage}
\caption{Spectra and best-fit model for nine bursts seen by the VLA from 2.5 to 3.5~GHz. Starting at the top left (moving right and then down), they correspond to bursts on MJDs 57623, 57633.68, 57633.70, 57638, 57643, 57645, 57646, 57648, and 57649. The solid line is a best-fit Gaussian model found through MCMC modeling. Note that bursts are detected in 5~ms images generated from dedispersed visibilities.
\label{fig:spec}}
\end{center}
\end{figure*}

This analysis differs from traditional analysis in that it simultaneously models the spectral and temporal evolution of the burst. Since the burst crosses many time-frequency pixel boundaries, the temporal modeling is sensitive to temporal properties smaller than the 5~ms integration time. Table \ref{tab:spec} shows that the typical burst width is measured as $2\pm1$~ms (95\% confidence interval); the brightest burst (57633.68) has a temporal width of $2.05\pm0.02$~ms. The burst arrival times are typically measured with a precision of 1~ms; the brightest burst arrival time is measured with a precision of $\sim50\mu$s. Note that these errors are only accurate to the degree that the model represents the data. One potential bias in the model is that we do not model scintillation effects.

@@

The top panel of Figure \ref{fig:dmmodel} shows the 95\% confidence intervals on the DM for all nine VLA bursts as a function of burst time. The burst DMs are not consistent with any single value and tend to be larger than the long-term average of 560.5 pc cm$^{-3}$. The range and variance in DM observed by the VLA is similar to that reported for Arecibo observations of \frb\ in \citet{2016arXiv160308880S}. As noted before, this is consistent with the idea that the DM measured at low resolution (e.g., by the VLA) is defined by true (extrinsic) dispersion and some spectral structure that changes between bursts. The VLA data demonstrate that the burst-dependent DM effect is visible at frequencies near 3~GHz. Assuming a "true" DM of 560.5 pc cm$^{-3}$, the excess DM can be thought of as a frequency-dependent delay that varies between bursts with a delay rate up to 2~ms GHz$^{-1}$.
